---
title: "Interactive Map"
author: "Santiago Puentes Navas"
date: "1/3/2020"
output: html_document
---

```{r setup}
library(leaflet)
```

## My Map

The purpose of this map is to show you a simple view of the main four cities of my country (Colombia) with links to the Wikipedia articles about them. I will use leaflet to showcase both the markers and the population sizes (coded by circles of varying radii). For the population, the numbers will be divided by 1000 (i.e. data will be shown x1000 inhabitants) in order to avoid issues with the circle drawings:

```{r project, echo = FALSE}
cities_main = data.frame(
name = c("Bogotá","Cali","Medellín","Barranquilla"),
lat = c(4.6097102,3.4372201,6.2518401,10.9685402),
lng = c(-74.081749,-76.5224991,-75.563591,-74.7813187),
pop = c(7744,2252,2533,1274)
)



cities_info = c(
  "<a href = https://en.wikipedia.org/wiki/Bogot%C3%A1>Bogotá</a>",
  "<a href = https://en.wikipedia.org/wiki/Cali>Cali</a>",
  "<a href = https://en.wikipedia.org/wiki/Medell%C3%ADn>Medellín</a>",
  "<a href = https://en.wikipedia.org/wiki/Barranquilla>Barranquilla</a>"
)


cities_main %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup = cities_info) %>%
  addCircles(weight = 1,radius = cities_main$pop * 15)
```

